---
title: "A5 Part II (GenBank)"
author: "Rishona Vemulapalli (20164619)"
date: "2023-02-23"
output: html_document
---

```{r}
library(annotate)
```

Store sequence in a character vector.
```{r}
Seq <- "GCCTGATGGAGGGGGATAACTACTGGAAACGGTAGCTAATACCGCATGACCTCGCAAGAGCAAAGTGGGGGACCTTAGGGCCTCACGCCATCGGATGAACCCAGATGGGATTAGCTAGTAGGTGGGGTAATGGCTCACCTAGGCGACGATCCCTAGCTGGTCTGAGAGGATGACCAGCCACACTGGAACTGAGACACGGTCCAGACTCCTACGGGAGGCAGCAGTGGGGAATATTGCACAATGGGCGCAA"
```

Search for closest match on GenBank.
Generate allignment to confirm similarity. 
Determine if it is human or another organism. 
Write report in R Markdown explaining to the clinician whether this is something to be concerned about, using graphics with text to explain your analysis. Pay attention to professional formatting. 
NOTE: You may need to adjust the timeout= and hitListSize= parameters in the blastSequences() function.

<br>

Note: This is not working. I have tried everything and cannot seem to obtain a result before the BLAST times out (even after saying "y" when asked to wait another _ seconds.)
```{r}
SeqBlastDF <- blastSequences(x = "GCCTGATGGAGGGGGATAACTACTGGAAACGGTAGCTAATACCGCATGACCTCGCAAGAGCAAAGTGGGGGACCTTAGGGCCTCACGCCATCGGATGAACCCAGATGGGATTAGCTAGTAGGTGGGGTAATGGCTCACCTAGGCGACGATCCCTAGCTGGTCTGAGAGGATGACCAGCCACACTGGAACTGAGACACGGTCCAGACTCCTACGGGAGGCAGCAGTGGGGAATATTGCACAATGGGCGCAA", hitListSize = "5", timeout = 30, as = 'data.frame')
```

BLAST has determined this as seq MT509623.1	Yersinia pseudotuberculosis strain EB35 16S ribosomal RNA gene, partial sequence. I know we are not supposed to do this, but thought I'd include it anyway. This is bacteria (not human). 

