---
title: "A5 Analysis (Part I)"
author: "Rishona Vemulapalli (20164619)"
date: "2023-02-19"
output: html_document
---

### Setup:
```{r message = FALSE}
library(dplyr)
library(htmltools)
```

<br>

### Image of *Borrelia burgdorferi* bacteria from the internet:
```{r}
img(src = "https://www.bayarealyme.org/wp-content/uploads/2014/08/borrelia-burgdorferi.jpg")
```

<br>

### Wikipedia page about *Borrelia burgdorferi*:
https://en.wikipedia.org/wiki/Borrelia_burgdorferi

<br>

------------------------------------------------------------------------------------------------------------------------

### ANALYSIS

**Importing Sequences.csv file.**
```{r}
Sequences <- read.csv("Sequences.csv")
```

<br>

**Printing each sequence.**
```{r}
Sequences[1, ] # sequence 1 (HQ433692.1)
Sequences[2, ] # sequence 2 (HQ433694.1)
Sequences[3, ] # sequence 3 (HQ433691.1)
```

<br>

**Counting the number of each nucleotide (A, T, G, C) in each of the 3 sequences, then creating a table (new dataframe) displaying this data.**
```{r}
for (i in 1:nrow(Sequences)) {
  A_count <- nchar(gsub("[^A]", "", Sequences$Sequence))
  T_count <- nchar(gsub("[^T]", "", Sequences$Sequence))
  C_count <- nchar(gsub("[^C]", "", Sequences$Sequence))
  G_count <- nchar(gsub("[^G]", "", Sequences$Sequence))
  NucleotideCounts <- data.frame("Sequence_ID" = c("HQ433692.1", "HQ433694.1", "HQ433691.1"),
                                 A_count, T_count, C_count, G_count)
}

print(NucleotideCounts)
```

<br>

**Calculating GC content (% of nucleotides that are G or C) and creating a table to show GC content for each sequence ID.**
Note: I understand that the way this is calculated is incorrect, as it is only pulling the first values, instead of running through the rest of the rows. I nonetheless have included my code below. 

When I calculated it by hand, I got these values for GC content:

- First sequence's GC content = 44.28%.
- Second sequence's GC content = 44.07%. 
- Third sequence's GC content = 44.07%. 

```{r}
NC <- NucleotideCounts[, 2:5]

for (i in 1:row(NC)) {
  GC_content <- round((sum(c(G_count, C_count))) / sum(c(A_count, T_count, G_count, C_count)) * 100, 2)
  GC <- data.frame("Sequence_ID" = NucleotideCounts$Sequence_ID, GC_content)
}

print(GC)
```

<br>
